---
title: "PCR-data"
output: html_document
---



Here I will attempt to get the PCR Data in order...

>You can easily add the dates. Any crab with a 37- or 38- prefix in the sample no. was from Day 26 -- those also have tube #s, cuz the aliquots (DNA in RNAlater) came from you. All the crabs with 30- thru 34- were sampled on day 0/1. Make sense?

File: https://raw.githubusercontent.com/RobertsLab/project-crab/master/data/20180522-master-qPCR-all-runs.csv




```{r}
first_pcr <- read_csv("../data/20180522-master-qPCR-all-runs.csv")
```

```{r}
first_pcr
```



```{r}
library(dplyr)
```


>You can easily add the dates. Any crab with a 37- or 38- prefix in the sample no. was from Day 26 -- those also have tube #s, cuz the aliquots (DNA in RNAlater) came from you. All the crabs with 30- thru 34- were sampled on day 0/1. Make sense?


```{r}
withDay <- mutate(first_pcr, sampleday = ifelse(Sample_pre == 37 | Sample_pre == 38, "day26", ifelse(Sample_pre == 30 | Sample_pre == 31 | Sample_pre == 32 | Sample_pre == 33 | Sample_pre == 34, "day01", "unknown"))) %>%
  group_by(FRP) %>% 
  mutate(grouped_id = row_number()) %>%
  spread(grouped_id, SQ_Mean)

```


Now need to work on getting FRP unique in every row...


```{r}
withDay02 <- mutate(first_pcr, sampleday = ifelse(Sample_pre == 37 | Sample_pre == 38, "day26", ifelse(Sample_pre == 30 | Sample_pre == 31 | Sample_pre == 32 | Sample_pre == 33 | Sample_pre == 34, "day01", "unknown"))) 

```

```{r}
write.csv(withDay02, "../analyses/withDay02.csv")
```



EXCDEL


```{r}
withDay03 <- read_csv("../analyses/withDay03.csv")
```


```{r}
withDay03[,2] <- sapply(withDay03[,2], as.integer)
```


]

```{r}
withDay03
```






```{r}
withDay03 %>%
  group_by(FRP) %>% 
  spread(sampleday, Starting_Quantity) 

```

```{r}
withDay03 %>%
  group_by(FRP) %>% 
  spread(sampleday, Starting_Quantity) %>% 
  summarise(avg = mean(Starting_Quantity))

```



```{r}
withDay03 %>%
  group_by(FRP) %>% 
  summarise(avg = mean(Starting_Quantity))

```